Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on fixes

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the official
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}.\Comment{ This test suite contains
  87\% of all the tests we used.} We also considered test suites of
three of the four engines mentioned in
Section~\ref{sec:methodology:engines} and four other engines. Overall,
we selected a total of \totfiles{} JS
files. Table~\ref{tab:test-suites} shows the breakdown of tests we
considered. Column ``original'' shows the number of test cases for
each test suite. We did not consider tests from the \chakra{}
repository because they depend on non-portable objects. Notice that
the number of tests in \veight\ is low. That happens because \veight{}
uses many tests from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. The columns
``compile-in-all'' and ``no-fail-in-all'' indicate the tests used in
the test transplantaion experiment and the differential testing
experiment, respectively.

@@

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc{} defines a function with a tail-call
recursion. The test fails in all engines but \jsc{}, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} does not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}.
%% \Mar{igor,
%%   nao consigo entender o porque deste caso nao dar aqueles erros
%%   (ReferenceError/TypeError) que vc. me mostrou e estourar na
%%   assercao. explique e de um exemplo concreto, por favor$\rightarrow$
%% }
%% \Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
%% diferente da que usamos anteriormente. Por exemplo, existem testes que 
%% estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
%% o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
%% }
\textbf{Non-Standard Element.} These cases manifest when a function or
an object property is undefined in the execution engine but we were
unable to capture looking for error types like \CodeIn{ReferenceError}
and \CodeIn{TypeError}. For example, we found cases where the test (or
its harness) capture the corresponding exception, making the test to
fail in an assertion instead. \Mar{igor, ha alguma explicacao/intuicao
  para explicar porque nao conseguir classificar isto?.$\rightarrow$}
  \Igor{Exemplos: Testes especificos e/ou com entradas invalidas, 
  por exemplo cobre uma especificacao antiga onde o
  teste esperava uma propriedade true, mas na documentacao 
  cita que a propriedade tem que ser false.}\Mar{nao
  entendi. isto nao acabaria quebrando por um dos motivos anteriores?
  seja mais especifico, por favor!}  \textbf{Unknown.} This category
includes the cases we were unable to confidently diagnose the failure
but we suspected it was a false alarm.

@@

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:test-transplantation-bugs}.}
Esse bug foi reportado no engenho do \chakra{} e foi manifestado atraves 
de uma mutacao provinda do \radamsa{}. O test case eh descrito in Figure~\ref{xxx},
the

>>>>

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the official
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}.\Comment{ This test suite contains
  87\% of all the tests we used.} We also considered test suites of
three of the four engines mentioned in
Section~\ref{sec:methodology:engines} and four other engines. Overall,
we selected a total of \totfiles{} JS
files. Table~\ref{tab:test-suites} shows the breakdown of tests we
considered. Column ``original'' shows the number of test cases for
each test suite. We did not consider tests from the \chakra{}
repository because they depend on non-portable objects. Notice that
the number of tests in \veight\ is low. That happens because \veight{}
uses many tests from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. The columns
``compile-in-all'' and ``no-fail-in-all'' indicate the tests used in
the test transplantation experiment and the differential testing
experiment, respectively.

@@

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc{} defines a function with a tail-call
recursion. The test fails in all engines but \jsc{}, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} does not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}.
%% \Mar{igor,
%%   nao consigo entender o porque deste caso nao dar aqueles erros
%%   (ReferenceError/TypeError) que vc. me mostrou e estourar na
%%   assercao. explique e de um exemplo concreto, por favor$\rightarrow$
%% }
%% \Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
%% diferente da que usamos anteriormente. Por exemplo, existem testes que 
%% estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
%% o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
%% }
\textbf{Non-Standard Element.} These cases manifest when a function or
an object property is undefined in the execution engine but we were
unable to capture looking for error types like \CodeIn{ReferenceError}
and \CodeIn{TypeError}. For example, we found cases where the test (or
its harness) capture the corresponding exception, making the test to
fail in an assertion instead. \Mar{igor, ha alguma explicacao/intuicao
  para explicar porque nao conseguir classificar isto?.$\rightarrow$}
  \Igor{Exemplos: Testes especificos e/ou com entradas invalidas, 
  por exemplo cobre uma especificacao antiga onde o
  teste esperava uma propriedade true, mas na documentacao 
  cita que a propriedade tem que ser false.}\Mar{nao
  entendi. isto nao acabaria quebrando por um dos motivos anteriores?
  seja mais especifico, por favor!}
  \Igor{nao, o teste eh valido (nao quebra por ReferenceError/TypeError) e
  nao entra no undefined behaviour pq nao afeta a especificacao. Isso eh um caso,
  outros casos estao ligados a nao-compreensao do testcase }  \textbf{Unknown.} This category
includes the cases we were unable to confidently diagnose the failure
but we suspected it was a false alarm.

@@

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:test-transplantation-bugs}.}
\Igor{JSC transplantation...}
